Manuscript title

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

###CLASS IMBALANCE HINDERS PERFORMANCE ACROSS RESOLUTIONS

Figure 11 present the results across all of the ensemble systems for each resolution of domain data. The first row in each of the 4 regions shows the performances for models without resampling. The average accuracy and AUC were marginally high across each of the resolutions with values of W%, X%, Y%, and Z% respectively. However, the severity of the model performances were much more apparant when comparing F1-scores and MCCs. The average F1-scores across resolutions for models without resampling were found to be W%, X%, Y%, and Z% respectively, while the MCCs were W%, X%, Y%, and Z% (Table 7). We thus see the necessity for implementing a class balancing technique prior to modeling.

###CLASS BALANCING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS

>>>>

###CLASS IMBALANCE HINDERS PERFORMANCE

We first compared models with either overlap counts or overlap percent predictor types, from the 5kb resolution data (Figure 12). These results were from random forest models fit to data without any re-sampling, using either LASSO or Elastic-Net regulariations. We found that differences in performances across variable reduction technique were marginal. However, when evaluating model performance using accuracy or AUC, the model appeared to perform relatively well. At second glance, though, when considering both the F1-score and MCC of the model, we were able to assess just how poorly the model was indeed performing (Supplementary Table 9). The low, and sometimes missing, values indicate that the model is unable to identify many, if any, true positive outcomes. That is, given an imbalanced data, the model is unable to predict which genomic bins truly contain a flanked TAD boundary. The performance results were found to be consistently poor for models with no re-sampling across the other resolutions (Supplementary Figure 13).

###Random UNDER-SAMPLING IMPROVES MODEL PERFORMANCE IN ALL RESOLUTIONS
